%
% LaTeX Problem Set Template 
%

%%%%%%%%PACKAGES%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\documentclass{article}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{amsthm}
\usepackage{amssymb}
\usepackage{mathdots}
\usepackage{mathtools}
\usepackage[pdftex]{graphicx}
\usepackage{fancyhdr}
\usepackage[margin=1in]{geometry}
\usepackage{multicol}
\usepackage{bm}
\usepackage{listings}
\PassOptionsToPackage{usenames,dvipsnames}{color}  %% Allow color names
\usepackage{pdfpages}
\usepackage{algpseudocode}
\usepackage{tikz}
\usepackage{enumitem}
\usepackage[T1]{fontenc}
\usepackage{inconsolata}
\usepackage{framed}
\usepackage{wasysym}
\usepackage[thinlines]{easytable}
\usepackage{hyperref}
\usepackage{wrapfig}
\usepackage[makeroom]{cancel}
\usepackage{tikz, wasysym}
\usepackage{minted}
\usetikzlibrary{automata,positioning, arrows.meta, calc}
\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    filecolor=magenta,
    urlcolor=blue,
}
\delimiterfactor = 1200
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\title{CMSI 3802: Languages \& Automata \\ Homework 5}
\author{[Ryan Ramsdell (980388983)]}
\date{\today}
\makeatletter
\let\runauthor\@author
\makeatother

\lhead{\runauthor}
\chead{HW 4}
\rhead{\today}
\lfoot{}
\rfoot{\thepage}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% start MZ
\let\oldemptyset\emptyset
\renewcommand{\emptyset}{\text{\O}}
\renewcommand{\labelitemii}{$\bullet$}
\renewcommand\qedsymbol{$\blacksquare$}
\newenvironment{prf}{{\bfseries Proof.}}{\qedsymbol}
\renewcommand{\emph}[1]{\textit{\textbf{#1}}}
\newcommand{\annotate}[1]{\textit{\textcolor{blue}{#1}}}
\usepackage{mdframed}
\usepackage{float}
\usepackage[dutchcal, slant]{suppose}

\makeatother
% end MZ

\definecolor{shadecolor}{gray}{0.95}

\renewcommand{\headrulewidth}{0.4pt}
\renewcommand{\footrulewidth}{0.4pt}

\setlength{\parindent}{0pt}

\pagestyle{fancy}

\renewcommand{\thefootnote}{\fnsymbol{footnote}}

\DeclarePairedDelimiter{\ceil}{\lceil}{\rceil}
%%%%%%%%%%%%%%%%Document Begins Here!%%%%%%%%%%%%%%%%%%%%%%%%
\begin{document}
\maketitle

\section*{Problem 1}
\begin{enumerate}[label=(\alph*)]
  \item Canadian Postal Codes
    \begin{shaded}
      \begin{minted}[autogobble]{js}
        /^[A-CDEGHJ-NPR-TV-Z]\d[A-CDEGHJ-NPR-TV-Z] \d[A-CDEGHJ-NPR-TV-Z]\d$/
      \end{minted}
    \end{shaded}
  \item Visa
    \begin{shaded}
      \begin{minted}[autogobble]{javascript}
        /^4(\d{15}|\d{12})$/
      \end{minted}
    \end{shaded}
  \item Mastercard
    \begin{shaded}
      \begin{minted}[autogobble]{javascript}
        /^(5[1-5]\d{2}|222[1-9]|22[3-9]\d|2[3-6]\d{2}|27[01]\d|2720)\d{12}$/
      \end{minted}
    \end{shaded}
  \item Strings of Unicode letters except those strings that are exactly three letters ending with two Latin letter o’s, of any case.
    \begin{shaded}
      \begin{minted}[autogobble]{javascript}
        /^(?!.o{2}$)\p{L}*$/iu
      \end{minted}
    \end{shaded}
  \item Binary numerals divisible by 16.
    \begin{shaded}
      \begin{minted}[autogobble]{javascript}
        /^(((?!0{4}$)[01])*0{4}|0+)$/
      \end{minted}
    \end{shaded}
  \item Decimal numerals in the range 8 through 32, inclusive.
    \begin{shaded}
      \begin{minted}[autogobble]{javascript}
        /^([89]|[12]\d|3[0-2])$/
      \end{minted}
    \end{shaded}
  \item All strings of Unicode letters, except \verb+python+, \verb+pycharm+, or \verb+pyc+.
    \begin{shaded}
      \begin{minted}[autogobble]{javascript}
        /^(?!py(thon|c?(harm)?)$).*$/u
      \end{minted}
    \end{shaded}
    \item Floating point constants that are allowed to have an empty fractional part, but whose exponent part is required and can have no more than three digits in the exponent part.
    \begin{shaded}
      \begin{minted}[autogobble]{javascript}
        /^\d+(.\d+)?e[+-]?\d{1,3}$/i
      \end{minted}
    \end{shaded}
    \item Palindromes over the letters a, b, and c, of length 2, 3, 5, or 8
    \begin{shaded}
      \begin{minted}[autogobble]{javascript}
        /^(?:([abc]?)([abc]?)([abc])[abc]\3\2\1|([abc]?)([abc]?)([abc]?)([abc])\7\6\5\4)$/
      \end{minted}
    \end{shaded}
    \item Python string literals.
    \begin{shaded}
      Ignore the line breaks, it won't fit on the page without them.
      \begin{minted}[autogobble]{text}
        /^(?:(?:br|Br|bR|BR|rb|rB|Rb|RB|b|B|r|R|u|U|f|F|fr|Fr|fR|FR|rf|rF|Rf|RF)?
        (?:'''(?:\\.|[^\\']|'{1,2}(?!'))*'''
        |"""(?:\\.|[^\\"]|"{1,2}(?!"))*"""|'(?:\\.|[^\\\n'])*'|"(?:\\.|[^\\\n"])*"))$/
      \end{minted}
    \end{shaded}
\end{enumerate}

\section*{Problem 2}
Show the language $\{ \hat{M_1}\{\cdot\}\hat{M_2} \mid L(M_1) = L(M_2) \}$ is undecidable, using a rigorous reduction argument.
\begin{shaded}
  \begin{proof}
    Let $\kappa = \{ \hat{M_1}\{\cdot\}\hat{M_2} \mid L(M_1) = L(M_2) \}$. \\
    I will demonstrate that if $\kappa$ is decidable, that would mean that the equality of the Turing machines $M_1$ and $M_2$ would have to be decidable, which is not the case. \\
    \begin{enumerate}
      \item $\csup \exists$ a decider, $D$ for $\kappa$. 
      \item To determine if $L(M_1) = L(M_2)$, for any Turing machines $M_1$ and $M_2$, we can create the string $\hat{M_1} \{\cdot\} \hat{M_2}$ and pass it to $D$.
      \item If $D$ accepts, then $L(M_1) = L(M_2)$, otherwise $L(M_1) \neq L(M_2)$.
      \item Due to the undecidability of the Turing machine equality problem, $\nexists D$ for $\kappa$.
      \item $\therefore$ $\kappa$ is undecidable.
    \end{enumerate}
  \end{proof}
\end{shaded}

\end{document}